Interpretable Neural Networks using EAGGA

### 2025-03-15 paper/main.tex
check references

\section{Introduction}
Regularisation has been extensively shown to improve performance from linear models to neural networks.
One of the most popular types of regularisation, Ridge or L2-regularisation is still the preferred method for handling
multicollinear data in linear models \citep[p. 55]{ridge}.
Practicioners training neural networks regularly use regularisation methods such as dropout to reduce
co-adaptation \citep[p. 1]{hinton2012improvingneuralnetworkspreventing} or early stopping to avoid overfitting on the training data \citep[p. 778f]{early_stopping}.
\\
Some regularisation can even increase interpretability, such as LASSO, or L1-regularisation for linear models, which reduces the number of
features used to fit the model by setting some coefficients to 0 \citep[p. 267]{lasso}.
\\
Neural networks as a model class have achieved impressive performance on a multitude of problems, yet still struggle with the most common format --
tabular data \citep[p. 7499]{Borisov_2024}.
Recent research, however, suggest that strong regularisation is beneficial to a neural network's performance on tabular data \citep[8]{NEURIPS2021_c902b497}.
\citet{EAGGA} propose a framework to increase the interpretability of XGBoost using regularisation.
In this report, we explore if the same framework can be extended to neural networks, a model class that in its fully-connected feedforwad form is
inherently non-interpretable, to tackle both explainability and achieve performance on tabular data that is on par with XGBoost.

@@

\subsection{Interpretability}
As there is no clear definition for interpretability, we will consider it as ``the ability to provide \textit{explanations} in \textit{understandable terms} to a human'',
where \textit{explanations} are logical decision rules and \textit{understandable terms} relate to commonly used terms in the domain of the problem,
as suggested by \citet[chap. 1]{survey_NN_interpretability}. Further, we use the term ``explainability'' in an exchangeable manner with ``interpretability'',
as is commonly done.

% Why Interpretability is desirable?
Explainability of a model's reasoning is in many ways desirable. \citet[pp. 3-4]{Zach2019InterpretabilityOD} gives a range of examples,
amongst which are \textit{gaining trust}, e.g. when doctors rely on medical diagnosis predictions, avoiding \textit{subconcious biases} by
making sure loan approvals are non-discriminatory, or \textit{regulatory} reasons, most notably the EU's ``Right to Explanation'' warranted by the
GDPR \citep[p. 1]{review_NN_interpretability} or for approval of drugs discovered using machine learning models \citep[1B]{survey_NN_interpretability}.
It can further prove helpful for explaining unexpected drops in model performance, which could arise from optimizing a model with respect to loss and then judging its
performance on a different metric such as accuracy, a practice known as \textit{model debugging} \citep[1B]{survey_NN_interpretability} or for
\textit{scientific understanding} in domains where only models can make sense of increasingly complex data anymore and learnt knowledge encoded in a model needs to be
made accessible to humans to be used reliably \citep[p. 1]{review_NN_interpretability}.

@@

% Taxonomy
\citet[chap. 2]{survey_NN_interpretability} extend this distinction to a three-dimensional taxonomy, allowing for better categorisation of neural networks (NNs).
\\
\textbf{Passive vs Active Approaches}, where \textit{passive} are all post-hoc methods and \textit{active} methods actively change either the architecture or
training process to increase model interpretability.
\\
\textbf{Type of Explanations}, distinguishing between \textit{example} methods, providing concrete examples of what leads to a desired output, \textit{attribution}
methods that attribute the effect on the output for a specific feature, \textit{hidden semantic} methods, which explain the types of inputs particular neurons or layers
pick up on, and logical \textit{rules}, such as if-then clauses or tree-induced rules.
\\
\textbf{Local vs Global Interpretability}, ranging from \textit{local} methods providing explanations based on individual samples, \textit{semi-local} methods,
explaining model behaviour for sets of samples grouped by some criterion, to \textit{global} methods, which explain the network as a whole.

% Evaluation
Given its unclear definition, evaluating interpretability can be challenging. \citet[3]{DoshiVelez2017TowardsAR} propose a taxonomy to categorise
possible evaluation methods based on their rigorousness.
\\
\textbf{Application-grounded evaluation} evaluates interpretations directly with respect to the task, by having human experts evaluate the outcome and
is therefore the most expensive and time-consuming of the three approaches.
\\
\textbf{Human-grounded metrics} is similar to application-grounded evaluation in that a human still evaluates the interpretations, but tries to simplify the task
so that a layperson can do it. Human-grounded approaches are especially suitable if it's sufficient to validate the general concepts of a task. A typical evaluation
set-up in this category is binary forced choice, where the human evaluator chooses, which of two generated explanations he prefers.
\\
\textbf{Functionally-grounded evaluation} is the least rigorous, but easiest to implement of the three. It assess explanatory quality according to some
formally defined proxy for interpretability and is particularly useful in ranking different models if their model-class is already identified
(e.g. via human-grounded evaluation) to be interpretable. The main challenge for functionally-grounded evaluation is finding a good proxy.

@@

% model free
% grid + random search
The most basic model-free strategies for blackbox optimization are grid and random search.
In the latter, the user defines a range of interest for each HP and then evaluating points along a grid within the cartesian product of those.
This has the drawback of scaling extremely poorly in both number of HP dimensions and number of query points per range of interest.
Random search, on the other hand, randomly samples a value for each HP until it runs out of budget. Its explorative nature, ease of use, and no assumptions
about the model makes it a good baseline. It is also superior to grid search in cases were one or more HPs have little impact on model performance,
as for a given budget $B$, each HP will likely be queried with $B$ different values, whereas for grid search each HP will only be queried with $B^{1/N}$
different values for $N$ HPs. \citep[chap. 1.3]{feurer_hyperparameter_2019}

% evolutionary algorithms
Another popular class of model-free optimizers are evolutionary algorithms (EAs), which are conceptually simple and can handle even complex parameter spaces,
given appropriate implementation of operators.
EAs are iteratively evolving a population of individuals (an individual is simply a hyperparameter configuration) of size $\mu$, where in each iteration (generation),
$\lambda$\footnote{We distinguish between $\lambda\in\mathbb{N}$ when referring to the offspring size of EAs and $\boldsymbol\lambda\in\boldsymbol\Lambda$ when
referring to a hyperparameter configuration.} offspring are generated via three operators \citep[pp. 10-14]{genetic_algos}.
\\
\textbf{Reproduction} samples an individual from the population to reproduce with probability proportional to its fitnes. For HPO, fitness usually refers to the
performance metric the model resulting from the individual's HP configuration is evaluated on.
\\
\textbf{Crossover} selects two ``parents'' from the pool of reproducing individuals. An index $k$ is sampled at random and all HP values from
index $k$ on are swapped, yielding two new ``children'' individuals.
\\
\textbf{Mutation} randomly changes single HP values of an individual chosen for reproduction, e.g. by adding Gaussian noise to real values or flipping bits
on binary values.
\\
At the end of each generation, the EA keeps the best $\mu$ individuals, either only from the offspring (``$(\mu,\lambda)$-selection'') or more commonly from
population and offspring (``$(\mu+\lambda)$-selection''), which is also called an ``elitist'' strategy, as it's guaranteed to keep the best individual.
\citep[chap. 1.3]{feurer_hyperparameter_2019}

One of the most popular EA implementations is the ``Covariance Matrix Adaptation Evolution Strategy'' (CMA-ES).
It employs a multivariate normal distribution to generate offspring, for which the mean is a weighted average of the previous generation's individuals
and the covariance matrix similarly is the weighted covariance of the previous generation.
The weighing scheme for both is done in a way as to reproduce previously successful (i.e. selected) steps \citep[p. 8-11]{hansen2023cmaevolutionstrategytutorial}.

@@

to the set of queried points \citep[chap. 1.3.2]{feurer_hyperparameter_2019} and \citep[pp. 2f]{frazier2018tutorialbayesianoptimization}.

@@

with only a subset of the samples. \citep[chap. 1.3.2]{feurer_hyperparameter_2019}

@@

less, making them a popular alternative to Gaussian Processes. \citep[chap. 1.3.2]{feurer_hyperparameter_2019}

\subsection{Neural Architecture Search}
A special case of HPO is Neural Architecture Search (NAS). Because of the flexibility of neural network architectures (number of hidden layers, strength of dropout,
each layer can have a different numer of neurons, each layer can have a different activation function, etc.), traditional HPO methods cannot efficiently explore the
entire space.
In our extension of the EAGGA approach we don't employ NAS as research focusses on the NLP and
image domains \citep{baker2017designingneuralnetworkarchitectures},  \citep{10.5555/3504035.3504375},  \citep{10.1145/3071178.3071229},
where features (i.e. tokens or pixels, respectively) exhibit strong correlation amongst themselves, which is usually not the case for tabular data \citep[p. 7499]{Borisov_2024}.
Still, we want to outline two notable approaches for neural architecture search in this paper, one of which are \textbf{cell search spcaces}.
These modularise an NN into a chain-structure of cells, where each cell is a basic building block of the respective architecture. For regular feedforwad neural networks,
this could be a linear layer of fixed size and with a specific activation function,
for CNNs this could be a specific convolutional operation or pooling function, for instance.
Instead of tuning every hyperparameter, the sequential placement of the cells is then optimzed during NAS, e.g. via random search or Bayesian
Optimization. \citep[chap. 3.2]{elsken_neural_2019}
\\
Treating a neural network as a sequence of cells instead of one fixed entity further allows exploiting this structure with special sequential optimization techniques.
\citet[p. 3]{zoph2017neuralarchitecturesearchreinforcement} and \citet[pp. 2-4]{Zoph_2018_CVPR} propose a cell search method using RNNs and reinforcement learning.
The cells in their approach are not fixed, but have hyperparameters themselves, such as the filter size and the stride size of a convolutional layer.
These hyperparameters are then predicted sequentially, given all the already predicted hyperparameters of previous layers. The RNN is trained using reinforcement
learning, where the actions are the different values the network can predict for a given hyperparameter and the reward function is the RNN's performance on held-out
validation data.
\\
The second approach to NAS is the \textbf{one-shot model}, which trains a ``fabric'', which can be understood as a DAG comprising all architectures of a given
search space. Each path through the DAG is one specific network architecture, where the nodes represent a layer of neurons and the edges in-between are operations
on the layers' values. The entire DAG has one designated input and one output node.
It is then trained just like a regular NN, after which the optimal path, i.e. network architecture, is selected from the fabric.
This has the advantage of, albeit being slower than training a single model, being far more efficient and less expensive than training all architectures encoded
in the fabric. \citep[pp. 1-2, p.8]{saxena2017convolutionalneuralfabrics}
% don't necessarily talk about co-adaptation problem

@@

\textbf{Scalarization} approaches impose an implicit order of priority on the objectives.
The simplest one is optimizing a weighted sum of objective functions
\begin{equation}
  \argmin_{\boldsymbol\lambda\in\boldsymbol\Lambda} \sum_{i=1}^m w_i c_i(\boldsymbol\lambda)
  \text{ s.t. } \sum_{i=1}^m w_i=1 \wedge w_i>0,\forall i=1,...,m
  \label{eq-a-priori-scalarization-weighted-sum}
\end{equation}
Weights are chosen a-priori by the user and the solution is very sensitive to them, making this method very reliant on different
users' preferences. \citep[p. 11]{10.1145/3610536} and \citep[chap. 3.1]{NSGA}
\\
Another form of scalarization is the $\epsilon$-constraint, which translates all but one objective into constraints and then optimizes the remaining
objective subject to the constraints. Without loss of generality, the first constraint can be optimized
\begin{equation}
  \argmin_{\boldsymbol\lambda\in\boldsymbol\Lambda} c_1(\boldsymbol\lambda)
  \text{ s.t. } c_2(\boldsymbol\lambda)\le\epsilon_2,...,c_m(\boldsymbol\lambda)\le\epsilon_m
  \label{eq-a-priori-scalarization-epsilon}
\end{equation}
This method is, similarly to the weighted sum, conceptually simple yet also very sensitive to the chosen constraints. \citep[p. 12]{10.1145/3610536}
\\
Alternative to scalarization is the \textbf{lexicographic method}.
For it, the user assigns a priority to each objective and then greedily optimizes each objective in order of priority, constrained to the solutions of
the already optimized, higher-priority objectives. \citep[p. 13749]{lexicographic_MOO}
Again, solutions are very dependent on the user-defined priorisation.

@@

      10 replications. Bars represent standard errors. \citep[Figure 2, p. 544]{EAGGA}}

@@

As evident from Figures \ref{fig-test-dhvs}, \ref{fig-eagga-xgb-dhvs}, applying EAGGA to neural networks yields comparable performance to applying it to XGBoost,
both with and without restricting the maximum tree depth.

@@

% belongs in "general algorithm"
%    - preliminary
%  * our implementation of feature + interaction detectors likely tend to include
%    - more features + interactions for high p datasets
%    - less for low p datasets
%    - remember: original paper samples \# of features included from truncated geometric distribution, what is not mentioned is probability of this distribution
%      is determined from fitting 10 trees + looking at relative \# of features used (cf. their github repo ~/R/TunerEAGGA.R function get\_n\_selected\_rpart())
%    -> mlr3 default decision tree max depth 30
%      * i.e. datasets with p < 30 might use all features, which translates to trunc geom prob = 1
%      * vice-versa for p >> 30 datasets relative \# features < 0.5 (our trunc geom prob)
%      * similar reasoning for pairwise interactions

\section{Conclusion and Future Outlook}
% Conclusion
The EAGGA framework has been shown to be able to preserve performance while increasing interpretabiltiy of XGBoost models on tabular data, which has long been 
a challenging discipline for neural networks. Following recent research suggesting that regularisation can improve NN performance on
tabular data \citep[8]{NEURIPS2021_c902b497}, we extend EAGGA \citep{EAGGA} to neural networks, utilising its regularising properties to achieve similar
performance with neural networks as with XGBoost and simultaneously increase interpretability of this notoriously uninterpretable model class.
As a consequence, we propose a new architecture allowing to model the equivalence relations of the EAGGA framework.
We create a model whose interpretation is active, attributional, and global in the framework of \citet[chap. 2]{survey_NN_interpretability}, and find
overall performance, as measured on the dominated hypervolume of (AUC, NF, NI, NNM) to be comparable to that of XGBoost fitted using EAGGA.
\\

>>>>

\section{Introduction}
Regularisation has been extensively shown to improve performance from linear models to neural networks.
One of the most popular types of regularisation, Ridge or L2-regularisation is still the preferred method for handling
multicollinear data in linear models \citep[p. 55]{ridge}.
Practicioners training neural networks regularly use regularisation methods such as dropout to reduce
co-adaptation \citep[p. 1]{hinton2012improvingneuralnetworkspreventing} or early stopping to avoid overfitting on the training data \citep[p. 778f]{early_stopping}.
\\
Some regularisation can even increase interpretability, such as LASSO, or L1-regularisation for linear models, which reduces the number of
features used to fit the model by setting some coefficients to 0 \citep[p. 267]{lasso}.
\\
Neural networks as a model class have achieved impressive performance on a multitude of problems, yet still struggle with the most common format --
tabular data \citep[p. 7499]{Borisov_2024}.
Recent research, however, suggest that strong regularisation is beneficial to a neural network's performance on tabular data \citep[p. 8]{NEURIPS2021_c902b497}.
\citet{EAGGA} propose a framework to increase the interpretability of XGBoost using regularisation.
In this report, we explore if the same framework can be extended to neural networks, a model class that in its fully-connected feedforwad form is
inherently non-interpretable, to tackle both explainability and achieve performance on tabular data that is on par with XGBoost.

@@

\subsection{Interpretability}
As there is no clear definition for interpretability, we will consider it as ``the ability to provide \textit{explanations} in \textit{understandable terms} to a human'',
where \textit{explanations} are logical decision rules and \textit{understandable terms} relate to commonly used terms in the domain of the problem,
as suggested by \citet[p. 726]{survey_NN_interpretability}. Further, we use the term ``explainability'' in an exchangeable manner with ``interpretability'',
as is commonly done.

% Why Interpretability is desirable?
Explainability of a model's reasoning is in many ways desirable. \citet[pp. 3f]{Zach2019InterpretabilityOD} gives a range of examples,
amongst which are \textit{gaining trust}, e.g. when doctors rely on medical diagnosis predictions, avoiding \textit{subconcious biases} by
making sure loan approvals are non-discriminatory, or \textit{regulatory} reasons, most notably the EU's ``Right to Explanation'' warranted by the
GDPR \citep[p. 1]{review_NN_interpretability} or for approval of drugs discovered using machine learning models \citep[pp. 727f]{survey_NN_interpretability}.
It can further prove helpful for explaining unexpected drops in model performance, which could arise from optimizing a model with respect to loss and then judging its
performance on a different metric such as accuracy, a practice known as \textit{model debugging} \citep[pp. 727f]{survey_NN_interpretability} or for
\textit{scientific understanding} in domains where only models can make sense of increasingly complex data anymore and learnt knowledge encoded in a model needs to be
made accessible to humans to be used reliably \citep[p. 1]{review_NN_interpretability}.

@@

% Taxonomy
\citet[pp. 728f]{survey_NN_interpretability} extend this distinction to a three-dimensional taxonomy, allowing for better categorisation of neural networks (NNs).
\\
\textbf{Passive vs Active Approaches}, where \textit{passive} are all post-hoc methods and \textit{active} methods actively change either the architecture or
training process to increase model interpretability.
\\
\textbf{Type of Explanations}, distinguishing between \textit{example} methods, providing concrete examples of what leads to a desired output, \textit{attribution}
methods that attribute the effect on the output for a specific feature, \textit{hidden semantic} methods, which explain the types of inputs particular neurons or layers
pick up on, and logical \textit{rules}, such as if-then clauses or tree-induced rules.
\\
\textbf{Local vs Global Interpretability}, ranging from \textit{local} methods providing explanations based on individual samples, \textit{semi-local} methods,
explaining model behaviour for sets of samples grouped by some criterion, to \textit{global} methods, which explain the network as a whole.

% Evaluation
Given its unclear definition, evaluating interpretability can be challenging. \citet[pp. 4-6]{DoshiVelez2017TowardsAR} propose a taxonomy to categorise
possible evaluation methods based on their rigorousness.
\\
\textbf{Application-grounded evaluation} evaluates interpretations directly with respect to the task, by having human experts evaluate the outcome and
is therefore the most expensive and time-consuming of the three approaches.
\\
\textbf{Human-grounded metrics} is similar to application-grounded evaluation in that a human still evaluates the interpretations, but tries to simplify the task
so that a layperson can do it. Human-grounded approaches are especially suitable if it's sufficient to validate the general concepts of a task. A typical evaluation
set-up in this category is binary forced choice, where the human evaluator chooses, which of two generated explanations he prefers.
\\
\textbf{Functionally-grounded evaluation} is the least rigorous, but easiest to implement of the three. It assess explanatory quality according to some
formally defined proxy for interpretability and is particularly useful in ranking different models if their model-class is already identified
(e.g. via human-grounded evaluation) to be interpretable. The main challenge for functionally-grounded evaluation is finding a good proxy.

@@

% model free
% grid + random search
The most basic model-free strategies for blackbox optimization are grid and random search.
In the latter, the user defines a range of interest for each HP and then evaluating points along a grid within the cartesian product of those.
This has the drawback of scaling extremely poorly in both number of HP dimensions and number of query points per range of interest.
Random search, on the other hand, randomly samples a value for each HP until it runs out of budget. Its explorative nature, ease of use, and no assumptions
about the model makes it a good baseline. It is also superior to grid search in cases were one or more HPs have little impact on model performance,
as for a given budget $B$, each HP will likely be queried with $B$ different values, whereas for grid search each HP will only be queried with $B^{1/N}$
different values for $N$ HPs. \citep[pp. 7f]{feurer_hyperparameter_2019}

% evolutionary algorithms
Another popular class of model-free optimizers are evolutionary algorithms (EAs), which are conceptually simple and can handle even complex parameter spaces,
given appropriate implementation of operators.
EAs are iteratively evolving a population of individuals (an individual is simply a hyperparameter configuration) of size $\mu$, where in each iteration (generation),
$\lambda$\footnote{We distinguish between $\lambda\in\mathbb{N}$ when referring to the offspring size of EAs and $\boldsymbol\lambda\in\boldsymbol\Lambda$ when
referring to a hyperparameter configuration.} offspring are generated via three operators \citep[pp. 10-14]{genetic_algos}.
\\
\textbf{Reproduction} samples an individual from the population to reproduce with probability proportional to its fitnes. For HPO, fitness usually refers to the
performance metric the model resulting from the individual's HP configuration is evaluated on.
\\
\textbf{Crossover} selects two ``parents'' from the pool of reproducing individuals. An index $k$ is sampled at random and all HP values from
index $k$ on are swapped, yielding two new ``children'' individuals.
\\
\textbf{Mutation} randomly changes single HP values of an individual chosen for reproduction, e.g. by adding Gaussian noise to real values or flipping bits
on binary values.
\\
At the end of each generation, the EA keeps the best $\mu$ individuals, either only from the offspring (``$(\mu,\lambda)$-selection'') or more commonly from
population and offspring (``$(\mu+\lambda)$-selection''), which is also called an ``elitist'' strategy, as it's guaranteed to keep the best individual.
\citep[p. 188]{simon2013evolutionary}

One of the most popular EA implementations is the ``Covariance Matrix Adaptation Evolution Strategy'' (CMA-ES).
It employs a multivariate normal distribution to generate offspring, for which the mean is a weighted average of the previous generation's individuals
and the covariance matrix similarly is the weighted covariance of the previous generation.
The weighing scheme for both is done in a way as to reproduce previously successful (i.e. selected) steps \citep[pp. 8-11]{hansen2023cmaevolutionstrategytutorial}.

@@

to the set of queried points \citep[p. 9]{feurer_hyperparameter_2019} and \citep[pp. 2f]{frazier2018tutorialbayesianoptimization}.

@@

with only a subset of the samples. \citep[pp. 10f]{feurer_hyperparameter_2019}

@@

less, making them a popular alternative to Gaussian Processes. \citep[p. 12]{feurer_hyperparameter_2019}

\subsection{Neural Architecture Search}
A special case of HPO is Neural Architecture Search (NAS). Because of the flexibility of neural network architectures (number of hidden layers, strength of dropout,
each layer can have a different numer of neurons, each layer can have a different activation function, etc.), traditional HPO methods cannot efficiently explore the
entire space.
In our extension of the EAGGA approach we don't employ NAS as research focusses on the NLP and
image domains \citep{baker2017designingneuralnetworkarchitectures},  \citep{10.5555/3504035.3504375},  \citep{10.1145/3071178.3071229},
where features (i.e. tokens or pixels, respectively) exhibit strong correlation amongst themselves, which is usually not the case for tabular data \citep[p. 7499]{Borisov_2024}.
Still, we want to outline two notable approaches for neural architecture search in this paper, one of which are \textbf{cell search spaces}.
These modularise an NN into a chain-structure of cells, where each cell is a basic building block of the respective architecture. For regular feedforwad neural networks,
this could be a linear layer of fixed size and with a specific activation function,
for CNNs this could be a specific convolutional operation or pooling function, for instance.
Instead of tuning every hyperparameter, the sequential placement of the cells is then optimzed during NAS, e.g. via random search or Bayesian
Optimization. \citep[p. 67]{elsken_neural_2019}
\\
Treating a neural network as a sequence of cells instead of one fixed entity further allows exploiting this structure with special sequential optimization techniques.
\citet[p. 3]{zoph2017neuralarchitecturesearchreinforcement} and \citet[pp. 2-4]{Zoph_2018_CVPR} propose a cell search method using RNNs and reinforcement learning.
The cells in their approach are not fixed, but have hyperparameters themselves, such as the filter size and the stride size of a convolutional layer.
These hyperparameters are then predicted sequentially, given all the already predicted hyperparameters of previous layers. The RNN is trained using reinforcement
learning, where the actions are the different values the network can predict for a given hyperparameter and the reward function is the RNN's performance on held-out
validation data.
\\
The second approach to NAS is the \textbf{one-shot model}, which trains a ``fabric'', which can be understood as a DAG comprising all architectures of a given
search space. Each path through the DAG is one specific network architecture, where the nodes represent a layer of neurons and the edges in-between are operations
on the layers' values. The entire DAG has one designated input and one output node.
It is then trained just like a regular NN, after which the optimal path, i.e. network architecture, is selected from the fabric.
This has the advantage of, albeit being slower than training a single model, being far more efficient and less expensive than training all architectures encoded
in the fabric. \citep[pp. 1-2, p. 8]{saxena2017convolutionalneuralfabrics}
% don't necessarily talk about co-adaptation problem

@@

\textbf{Scalarization} approaches impose an implicit order of priority on the objectives.
The simplest one is optimizing a weighted sum of objective functions
\begin{equation}
  \argmin_{\boldsymbol\lambda\in\boldsymbol\Lambda} \sum_{i=1}^m w_i c_i(\boldsymbol\lambda)
  \text{ s.t. } \sum_{i=1}^m w_i=1 \wedge w_i>0,\forall i=1,...,m
  \label{eq-a-priori-scalarization-weighted-sum}
\end{equation}
Weights are chosen a-priori by the user and the solution is very sensitive to them, making this method very reliant on different
users' preferences. \citep[p. 11]{10.1145/3610536} and \citep[pp. 223f]{NSGA}
\\
Another form of scalarization is the $\epsilon$-constraint, which translates all but one objective into constraints and then optimizes the remaining
objective subject to the constraints. Without loss of generality, the first constraint can be optimized
\begin{equation}
  \argmin_{\boldsymbol\lambda\in\boldsymbol\Lambda} c_1(\boldsymbol\lambda)
  \text{ s.t. } c_2(\boldsymbol\lambda)\le\epsilon_2,...,c_m(\boldsymbol\lambda)\le\epsilon_m
  \label{eq-a-priori-scalarization-epsilon}
\end{equation}
This method is, similarly to the weighted sum, conceptually simple yet also very sensitive to the chosen constraints. \citep[p. 12]{10.1145/3610536}
\\
Alternative to scalarization is the \textbf{lexicographic method}.
For it, the user assigns a priority to each objective and then greedily optimizes each objective in order of priority, constrained to the solutions of
the already optimized, higher-priority objectives. \citep[p. 13749]{lexicographic_MOO}
Again, solutions are very dependent on the user-defined priorisation.

@@

      10 replications. Bars represent standard errors. Figure taken from \citep[Figure 2, p. 544]{EAGGA}}

@@

As evident from Figures \ref{fig-test-dhvs}, \ref{fig-eagga-xgb-dhvs}, applying EAGGA to neural networks yields similar or slightly worse performance compared to
to applying it to XGBoost, both with and without restricting the maximum tree depth.

@@

\section{Conclusion and Future Outlook}
% Conclusion
The EAGGA framework has been shown to be able to preserve performance while increasing interpretabiltiy of XGBoost models on tabular data, which has long been 
a challenging discipline for neural networks. Following recent research suggesting that regularisation can improve NN performance on
tabular data \citep[8]{NEURIPS2021_c902b497}, we extend EAGGA \citep{EAGGA} to neural networks, utilising its regularising properties to achieve similar
performance with neural networks as with XGBoost and simultaneously increase interpretability of this notoriously uninterpretable model class.
As a consequence, we propose a new architecture allowing to model the equivalence relations of the EAGGA framework.
We create a model whose interpretation is active, attributional, and global in the framework of \citet[pp. 3f]{survey_NN_interpretability}, and find
overall performance, as measured on the dominated hypervolume of (AUC, NF, NI, NNM) to be comparable to that of XGBoost fitted using EAGGA.
\\
